### 2017-11-09 paper/sections/3_methodology.tex
paper: addresses #10
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

>>>>

Mantle also provides functions for persisting state across decisions.
\texttt{WRState(s)} saves state \texttt{s}, which can be a number or boolean
value, and \texttt{RDState()} returns the state saved by a previous iteration.
For example, a ``when" policy can avoid trimming a cache or migrating data if
it had performed that operation in the previous decision using:

\begin{figure}[h]
\footnotesize
\begin{minted}{lua}
if RDState() == 1 then
  WRState(0)   -- the next decision will return true
  return false
else then
  WRState(1)   -- the next decision will return false
  return true
end
\end{minted}
\end{figure}
